% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{multicol}

\usepackage[scale=0.84]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, un to adjust the width of the space allocated to your name


%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Hollis} % Your first name
\familyname{Akins} % Your last name
% All information in this block is optional, comment out any lines you don't need
%\title{Physics Student}
\mobile{(336) 681-8118}
\email{hollis.akins@gmail.com}
\address{www.hollisakins.com\\Box 3039, 1115 8th Ave, Grinnell, IA 50112\\}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"To work in a firm with a professional work driven environment where I can utilize and apply my knowledge." -- Tarun}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\textit{Education}}

\cventry{fall 2018--}{Grinnell College}{Dean's Scholar}{Grinnell, IA}{}{
Intended Physics major, expected graduation May 2022\\
Current coursework includes Modern Physics, Differential Equations, and Video Production. 
Planned coursework for Spring 2019 includes Mechanics, General Relativity, Linear Algebra, Sociology, and Geographic Information Systems.
}

\cventry{2014--2018}{The Early College at Guilford}{}{Greensboro, NC}{}{
Public high-school dual-enrollment program with Guilford College\\
Coursework included a three-semester introductory physics sequence, computational physics, multivariable calculus, geographic information systems, experience design, observational astronomy, and several semesters of studio art.  
}



%----------------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\textit{Experience}}
%\section{Work Experience}
%\section{Research Experience}

%%%%
% Include different sections here as you see fit, re-order if necessary, comment out listing that do not apply
%%%%


\cventry{fall 2018--}{Staff Member}{Spencer Grill}{Grinnell, IA}{}{Helped with food and beverage preparation and customer service.  }

\cventry{summer 2018}{Research Assistant}{Guilford College Cline Observatory}{Greensboro, NC}{}{Worked with Professor Don Smith at Guilford College to develop an automated data analysis / photometry pipeline and scripted observer system for the permanently mounted 16-inch telescope at the Cline Observatory. 
This system facilitates current and future student research on variable stars, stellar evolution, the accuracy and precision of our facility, and more. See more at {\color{red}www.hollisakins.com}.}

\cventry{fall 2017}{Teaching Assistant}{Guilford College Art Dept.}{Greensboro, NC}{}{Served as a teaching assistant for the introductory darkroom photography class at Guilford College\\
Primary duties included conducting class demonstrations, helping students with their work outside of class, and maintaining the cleanliness and function of the photography lab facilities}

\cventry{2017--2018}{Barista}{Starbucks Coffee Company}{Greensboro, NC}{}{Worked as a certified Starbucks Barista preparing food and beverages, maintaining store cleanliness, and satisfying any and all customer needs}

\cventry{2016--2018}{Office Assistant}{Harris Teeter Supermarkets}{Greensboro, NC}{}{Assisted managers in supervising front-end operations by counting and handling the cash in the store, performing daily bookkeeping tasks, working at the customer service desk, and cashiering as needed}




\section{\textit{Selected Projects \& Awards}}

\cvitem{may 2018}{Co-wrote a paper with Don Smith at Guilford College on the pedagogical power of the Lucky Imaging technique for photographing planets, published in the Oct. 2018 issue of \textit{The Physics Teacher}. This project began as a presentation for the Guilford Undergraduate Symposium in Apr. 2018 and was modified for publication. See more at {\color{red} https://doi.org/10.1119/1.5055339.}}

\cvitem{2018--2019}{Recipient of the Dean's Scholarship and National Merit Scholarship at Grinnell College}

\cvitem{march 2018}{Honorable Mention in the SIAM Mathworks Math Modelling Challenge}

%\cvitem{2017--2018}{Member of the Early College at Guilford Chapter of the National Honor Society}


%----------------------------------------------------------------------------------------
%   OTHER THINGS
%----------------------------------------------------------------------------------------

\section{\textit{Skills}}

\cvitem{computer}{Experienced in Python, \LaTeX, GNU/Linux, and MacOS. Intermediate experience with HTML5/CSS3.}
\cvitem{}{Proficient in Adobe Photoshop, Illustrator, InDesign, and Premiere}
\cvitem{personal}{I am a detail-oriented independent learner, able to adapt quickly to new situations. I am responsible, disciplined, and reliable, and work well under pressure.}

\cvitem{interpersonal}{I work well on a team, working with other's ideas as well as contributing my own. I am able to communicate clearly, politely, and helpfully with others. }
%\cvitem{}{Experience and training in telescope use, ranging from small, portable telescopes to large, permanent telescopes to radio telescopes.}




%\section{\textit{References}}
%
%\begin{multicols}{2}
%\cvitem{name}{Don Smith}
%\cvitem{title}{Associate Professor, Guilford College}
%\cvitem{mail}{email@guilford.edu}
%\vfill\null
%\columnbreak
%\cvitem{name}{blah blah}
%\cvitem{title}{Professor, somewhere}
%\cvitem{mail}{email@institution.edu}
%
%\end{multicols}
%----------------------------------------------------------------------------------------
%   COVER LETTER
%----------------------------------------------------------------------------------------



%\clearpage
%
%\recipient{Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%\lipsum[1-3] % Dummy text
%\makeletterclosing % Print letter signature
 

\end{document}